% !TeX root = ../thuthesis-example.tex

% Your chapter title here
% Please make sure that the title is in CAPITALS
% All section and subsection headings, use capital letters where required
\chapter{INTRODUCTION}

\section{Problem definition}

Internet of Things (IoT) is expected to connect hundreds of billions of devices in less than a decade\cite{simiscuka_synchronisation_2018}, with tens of billions of connected IoT devices already exist in the world, and this number is anticipated to keep increasing as the Internet connectivity has become a standard feature for a great number of electronic devices\cite{hu_virtual_2021}. Many companies, such Huawei, Baidu, Alibaba, Tencent, Google, Intel and so on, already provide their own solutions for operating with data coming from IoT devices. Although most of the solutions by companies are restricted to be used only with the limited types or models of IoT devices, nonetheless, they may come to the standardization of IoT devices in the next few years. Even nowadays, most of the consumer IoT devices can be controlled by popular smart assistants, such as Apple Siri, Amazon Alexa, Tencent Xiaowei and others, or by SDKs, such as Apple HomeKit, which makes it possible to control the devices using our phones, computers or Smart Speakers.

On the other hand, controlling the IoT devices through proprietary buttons, screens, sliders located on ones, by smartphones or by smart speakers does not still provide the best user experience. The interaction techniques are very limited: even though the processing power per energy consumption has increased dramatically, and it is possible to have the processing power of high-performance PC of 1990s in tiny devices, such as smart watches, there is no freedom of movement and data sharing. Even though 5G networks partly solve the issue, for example by making it possible to create Internet of Vehicle (IoV), the transmission bandwidth is still limited, causing serious safety consequences\cite{hu_virtual_2021}. For example, when computations for interaction techniques, such as hand gesture recognition can not be performed on the IoT device due to its limited computing power, the sensing data can be transferred to the server, analyzed, and only after sent back to the sensing device to provide output for the user.

The sixth generation (6G) mobile network is expected to cast high-speed and high-efficiency transmission standards to adapt to the further development of new applications \cite{liao_information-centric_2021} \cite{huang_survey_2019}. It is expected for 6G network to be evolution of 5G network, and, therefore, provide faster data sharing between the devices, which will help to overcome the issues stated in the previous paragraph. As soon as it becomes possible, the companies, which adapt their solutions for the new standards faster, will be more successful on the IoT market. This leads to the assumption that the speed of the development in such case is one of the most important factors.

Currently, the common way of integrating IoT devices in the development stage inside the existing environment is to either use their virtual (or digital) twins, or by using their prototypes. In the first case, interaction with such devices is performed through a 2D interface, with a very rough simulation of the user behaviour, which leads to further underestimations. In the second case, creating a prototype requires waiting for the modeling of the IoT device, sending the schemes to the manufacturers, and then waiting for the prototype to be delivered. In both cases the disadvantages lead to possibility of losing the market, either because of lack of usability, or because of being too late to enter the market, already taken by the competitors. Companies and researchers need a devoid of these disadvantages instrument, to integrate prototypes of devices inside the existing real-world IoT environment.

In this study one of the solutions to this problem is proposed: a platform for developing new IoT devices. In the next section it is described how using another perspective technology can help to create such platform.

\section{Research idea and tasks}

\subsection{Using Virtual Reality to create a platform}